The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-10-12 paper.tex
add some more authors

@@

% alphabetical by last name
\author{Lincoln~J.~Greenhill} \harvard
\author{T.~Joseph~W.~Lazio}   \jpl
\author{David~P.~Woody}       \ovro

@@

\bibliographystyle{apj}
\bibliography{paper}

>>>>

\newcommand{\berkeley}{
    \affiliation{
        University of California Berkeley,
        501 Campbell Hall,
        Berkeley, CA 94720
    }
}

\newcommand{\swinburne}{
    \affiliation{
        Centre for Astrophysics \& Supercomputing,
        Swinburne University of Technology,
        PO Box 218,
        Hawthorn, VIC 3122, Australia;
    }
}

\newcommand{\vt}{
    \affiliation{
        Bradley Department of Electrical \& Computer Engineering,
        Blacksburg, VA 24061
    }
}

@@

% alphabetical by last name
\author{Steven~W.~Ellingson}  \vt
\author{Lincoln~J.~Greenhill} \harvard
\author{T.~Joseph~W.~Lazio}   \jpl
\author{Daniel~C.~Price}      \harvard \berkeley \swinburne
\author{David~P.~Woody}       \ovro

@@

\bibliographystyle{aasjournal}
\bibliography{paper}
